Cross-relaxation in dense ensembles of NV centers and application to magnetometry

### 2022-12-06 Talks/Soutenance 2022/presentation.tex
vf?

\subsection{Conclusion}
\begin{frame}{Conclusion}
\begin{itemize}
\item The use of NV center ensemble for magnetometry is currently limited by the interactions between the spin defects.
\pause
\bigskip
\item Dipole-dipole interaction within dense ensemble of NV centers result in spin depolarization. This effect is stronger in zero-field.
\pause
\bigskip
\item This depolarization can be used to perform microwave-free and orientation-free magnetometry at low magnetic field.
\pause
\bigskip
\item The physics of low-field depolarization is complex and need to be further studied to improve the performances of LFDM.
\end{itemize}

\end{frame}

@@

\section*{Bonus slides}

@@

@@

\begin{frame}{LFDM: shot-noise limit}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_bonus_shot_noise_limit}
\end{frame}

>>>>

\subsection{Conclusion}

\begin{frame}{Conclusion}
\end{frame}

\begin{frame}{Conclusion}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CCL_f-4}
\end{frame}

\begin{frame}{Conclusion}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CCL_f-3}
\end{frame}

\begin{frame}{Conclusion}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CCL_f-2}
\end{frame}

\begin{frame}{Conclusion}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CCL_f-1}
\end{frame}

\begin{frame}{Conclusion}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CCL_f}
\end{frame}

@@

%\section*{Bonus slides}

@@

\begin{frame}{LFDM: shot-noise limit}
\centering
\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{Slide_bonus_shot_noise_limit}
\end{frame}

\begin{frame}{Protocol T1}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_protocol}
\end{frame}

\begin{frame}{Protocol T1}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_exp_et_stretch}
\end{frame}

\begin{frame}{Fluctuator linewidth}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{slide_fluct_linewidth}
\end{frame}

@@
